Deep triplet network adopting the kernel and the range space learning for Wi-Fi signature verification

### 2019-07-11 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr: method_update_fig

\subsection{ConvNets with triplet input}
ConvNets with triplet input is widely used in face recognition \cite{schroff2015facenet} and person re-id \cite{cheng2016person,chen2017beyond}.
The distinction between classes may be ambiguous in the above tasks. This is because the targets may be looking in different directions or taking different positions.
Triplet ConvNets works by extract feature vectors which expand margins between same class and different class,so it has good ability to distinguish between classes.

but loss function depends on the distance between each triplet samples, loss can be down to 0, when negative class distance is much more greater than positive distance. also, outliers affects a lot to training.
so it is important to optimize the training process when traning triplet ConvNets.

@@

in this paper, we adopt the kernel and the range space learning to select good samples for training triplet ConvNets.
it has advantage for reducing computing resources, speed up training, and optimize training.

@@

In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter). An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.
Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our network. Subsequently, the training dataset is moved to KAR space learning. KAR space learning generates triplet data by mining the hard positve and hard negative samples for given anchor signal.
generated triplet data flows into ConvNet structure. ConvNet extracts feature vectors by using filters.
ConvNet training is achived by triplet loss, which is formulated by the L-2 distance of feature vectors for the triplet. 
The following subsections detail the proposed method.

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_network_structure.pdf}
    \caption{Structure of the network} \label{fig1}
\end{figure}

@@

Our proposed networks utilizes the L-2 distance to calculate the triplet loss for given triplet input. For the $i_{th}$ anchor input signal $\mathbf{I}_{i,anc}$, triplet input can be generated by grouping positive input signal $\mathbf{I}_{i,pos}$ and negative input signal $\mathbf{I}_{i,neg}$.
positive input is drawn from the same identity for anchor signal and negative input is chosen from another identity for the anchor.
Generated triplet $\left\{\mathbf{I}_{i,anc},\mathbf{I}_{i,pos},\mathbf{I}_{i,neg}\right\}$ is the input to the ConvNet structure.
Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure. The triplet loss for the inputs can be calculated as follows:

\begin{equation}
    loss = \sum_i^N { \left[ {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,pos}}} \right\|_2^2} -
    {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,neg}}} \right\|_2^2}  + \alpha \right]_+},
\end{equation}

where $\alpha$ is the margin between distances from anchor to positive and anchor to negative, N is size of the mini-batch. (+) means greater number between zero or calculated loss.

@@

% Dataset
\subsubsection{Dataset}
 To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
 % pre-processing
 Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy. Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action. Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals. As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
 % description
 we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).

% network shape

% network parameters

@@

>>>>

\subsection{ConvNets with triplet input}

ConvNets with triplet input is widely used in face recognition \cite{schroff2015facenet} and person re-id \cite{cheng2016person,chen2017beyond}.
The distinction between classes may be ambiguous in the above tasks. This is because the targets may be looking in different directions or taking different positions.
Triplet ConvNets works by extract feature vectors which expand margins between same class and different class, so it has good ability to distinguish between classes.

Loss function depends on the distance between each triplet samples, loss can be down to 0, when negative class distance is much more greater than positive distance. also, outliers affects a lot to training.
so it is important to optimize the training process when traning triplet ConvNets.

@@

in this paper, we adopt multilayer feedforward networks, trained by the kernel and the range space learning to select good samples for training triplet ConvNets.
it has advantage for reducing computing resources, speed up and optimize training.

@@

% Methods: System overview(Fig.1)
In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter). An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.

Essentially, the Wi-Fi signature signals are separated to create the training and validation data. Subsequently, KAR space projection learning generates triplet data by mining the hard positve and hard negative samples for given anchor signal from training dataset.

For training ConvNet structure, generated triplet data flows into ConvNet structure. ConvNet extracts feature vectors from given triplet.
ConvNet training is achived by triplet loss, which is formulated by the L-2 distance metrics of feature vectors. ConvNet network is trained by backpropagation. The following subsections detail the proposed method.

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v1}
    \caption{Structure of the network} \label{fig1}
\end{figure}

@@

Triplet loss is used to train ConvNet to extract feature vector better from triplet input.
For the $i_{th}$ anchor input signal $\mathbf{X}_{anc,i}$, triplet input is generated by grouping positive input signal $\mathbf{X}_{pos,i}$, which drawn from the same identity for anchor and negative input signal $\mathbf{X}_{neg,i}$, chosen from another identity for the anchor.
Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is fed into the ConvNet structure one by one and makes anchor, positive and negative feature vectors.

Let $\mathbf{v}_{anc,i}\in{\mathrm{R}}^{d\times1}$, $\mathbf{v}_{pos,i}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{v}_{neg,i}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.

triplet loss is calculated by comparing positive distance(L-2 distance from anchor to positive feature vector)and negative distance(L-2 distance from anchor to negative feature vector).
ConvNet is trained to maximize gap between positive distance to negative distance more than margin $\alpha$.

The triplet loss for the inputs can be calculated as follows:

\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right)
\end{equation}

where N is size of the mini-batch.
note that triplet loss can down to 0 when negative distance is longer than positive distance more than margin $\alpha$.
if we select proper triplet for training, we can avoid this problem and make convergence of the loss function faster. This can be done by selecting hard triplet.

@@

% Dataset
\subsubsection{Dataset}
 To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
 % pre-processing
 Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy. Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.

 Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals. As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
 % description
 we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).

@@

\subsubsection{Results}
\subsubsection{Training Efficiency}
